### 2018-06-07 documents/Referee Responses/refereeresponses.tex

    \response{
        Initially, the particular inflations considered were chosen with the intuition that ``larger'' inflations might be capable of generating new inequalities. Moreover, inflations ``larger'' than the Web inflation became computationally demanding for investigations. Overtime, more intuitions and insight began to develop. For example, the Wagon-Wheel inflation is not an arbitrary choice. In the Bell structure, both Alice $A$ and Bob $B$ have two settings. Therefore, in order to capture this idea in an inflation of the triangle structure, we needed to construct two copies of Alice $A_1$, $A_2$, and Bob $B_1$, $B_2$, and consequently two copies of settings variables $X_{1}, X_{2}$ and $Y_{1}, Y_{2}$. As pointed out in Section V, the role of Charlie $C$ is to document and announce all distinct pairs of settings and therefore at least four $C$'s are ``needed''. These observations suggest the Wagon-Wheel inflation is worth considering. In this sense, we might have expected the Wagon-Wheel inflation to be useful. At the moment, we have yet to develop a systematic and universal understanding of these vague intuitions and insights. Therefore, we elected to omit these imprecise discussions from the paper and have differed these ideas for future research.

        See also response \textbf{2.5}.
    }

    \ccomment{I'm not sure the figures of distributions are presented in the best way: given that (if I understand correctly) there are only 3 different values in Fig 5, for example, why not just state these individually (like is done for the white value) rather than give the scale of values.}

    \response{ Great point. Figures 4 and 5 have been tweaked to simply state the three probability values. }

    \ccomment{
    Sec VIII:

    "..initial parameters such that the initial point of the optimization was close to P\_F.": can you say more about what "close" means? Were all parameters varied or only the nonzero parameters?}

    \response{
        Here ``close'' means close with respect to a Euclidean norm in parameter space. These nearby points in parameter space were obtained by first constructing parameters which reproduce $P_{F}$ exactly. Then for each individual parameter $\lambda$ in this set, we sampled a perturbation $\de \lambda$ from a Gaussian distribution with standard deviation $\sigma = 2\pi 10^{\chi}$. Then we seeded the numerical optimization with $\lambda + \de \lambda$. If we let $\chi$ become too large (approximately $\chi > -1.5$), the numerical optimization would converge to parameters that generate saturating distributions. For $\chi$ sufficiently small, the optimization would converge to parameters that generate violating distributions. In this sense, all of the parameters were varied. Below is a plot illustrating this phenomena.
        \begin{center}
            \includegraphics[scale=0.4]{Gaussian_Perturbation_Fritz_Color_Default.pdf}
            \includegraphics[scale=0.4]{Gaussian_Perturbation_Fritz_Color_Zoomed.pdf}
        \end{center}
    }

    \ccomment{"...violating it suboptimally than P\_F.": reword}

    \response{Reworded sentence: ``To the contrary, our numerical optimization failed to find any symmetric quantum distributions capable of violating $I_{\text{SymmetricWeb}}$''.}

    \ccomment{
    Conclusions:

    Perhaps it is misleading to say that no noise is tolerated by Fritz's argument: his argument works for noisy entangled states (provided CHSH is still violated). Perhaps it is less obvious what happens when noise occurs elsewhere, but the other parts need only classical resources to realize in which case noise is less problematic. I would also imagine that even if it not literally robust as written that it could be made robust fairly easily.}

    \response{
        You are correct in saying that if the entangled quantum state shared between $A$ and $B$ is subjected to noise, then provided that CHSH is still violated, Fritz's argument still holds. Crucially however, the argument requires \textit{perfect} correlation between $C$ and the left bits of $A$ and $B$. Therefore, introducing \textit{any} amount of noise to the classical resources which establish these perfect correlations prohibits one from applying Fritz's argument with absolute confidence. Nonetheless, we \textit{are} sympathetic to sharing your intuition as a means of a priori expecting that \textit{some} amount of noise is tolerable, but the important question is how much noise? The robustification of Fritz’s argument is precisely what this paper accomplishes using the Inflation Technique. It is our hope that further research will identify a more direct/simple route for performing these robustifications in general.
    }

    \ccomment{grammar: "a causal compatibility inequalities"}

    \response{Corrected: ``...it was demonstrated that these causal compatibility inequalities are robust to noise...''.}

    \ccomment{"advantages from a resource perspective": it isn't clear to me what you are referring to, so please add some explanation or reword.}

    \response{
        Apologies for this confusion. An earlier draft had a more detailed explanation of what we mean by a ``resource perspective'' but subsequently omitted. As such, we have decided to remove this comment from the conclusion entirely. Remnants of these ideas have been re-introduced in the new section titled Revisiting Fritz’s Problem (see Response \textbf{1.14}).

        Specifically, the original idea was as follows. In order to find new examples of novel quantum resource in the Triangle structure, perhaps one might need to require the three parties $A,B,C$ to perform some correlation game/task using the latent resources of the Triangle structure. In particular, one could ask what correlations are achievable using only a single quantum state, or two quantum states, or all three. Since Fritz distribution can be achieved with only a single quantum state, maybe distributions which need to exploit the quantum resources of all three exhibit a type of non-classicality distinct from the Fritz distribution.
    }

    \ccomment{p14 typo: "which be solved"}

    \response{Corrected: ``...which can be solved efficiently...''.}
